---
title: "Package demo"
author: "William Shih, Ricardo Simpao, Nilay Varshney, Luke Yee"
date: "3/20/2020"
output:
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Here is an example of how our package functions run. For our data set, we are using a "SGEMM GPU kernel performance Data Set," which measures the running times of a matrix-matrix product, given different parameter combinations.

Below, all 4 functions (calculating linear regression bootstrap, calculating coefficient confidence intervals, prediction intervals, and confidene intervals for sigma^2) are much faster with C++ than R. Overhead with functions such as map, apply, and reduce take much longer than when compared to C++ version that only uses RcppArmadillo and functions from std namespace. Use of syntactic sugar from Rcpp is minimized in the C++ functions.

```{r load, message = FALSE, warning = FALSE}
library(devtools)
library(tidyverse)
library(STA141CFinal)
library(furrr)

set.seed(141)
dat = read_csv("sgemm_product.csv")
dat = dat[sample(241000, 1000),]
dat2 = dat[1:100,]
```

```{r linear regression with bootstrap, cache = TRUE}
#We specifiy a specific column set
y = dat$`Run1 (ms)`
x = dat[,1:(ncol(dat)-4)]

#linear model objects
fit = linear_reg_bs_C(x, y, s = 10, r = 1000)
```

# Linear Regression with blb (n = 1000, p = 15, subsets = 10, and replications = 1000)

```{r, echo = FALSE, cache = TRUE}
(b0 = bench::mark(
  linear_reg_bs(x = x, y = y, s = 10, r = 1000),
  linear_reg_bs_par(x = x, y = y, s = 10, r = 1000),
 linear_reg_bs_C(x, y, s = 10, r = 1000),
  check = FALSE)
)

ggplot2::autoplot(b0)
```

### The C++ version is about 10 times faster than either of the R versions. The C++ version uses RcppArmadillo to multiply matrices as that was found to be the fastest version available. RcppArmadillo was generally faster than using multiplying matrices using std::inner_product. The R parallel version took just as long as the R non-parallel version. 

# 95 % Confidence Interval for Variable Coefficients (original dataset has 1000 replications and 10 subsets)

```{r CI of coef, cache = TRUE}
coef_CI(fit, alpha = 0.05)

coef_CI_par(fit,alpha = 0.05)
coef_CI_C(fit,alpha = 0.05)


(b1 = bench::mark(
  coef_CI(fit, alpha = 0.05),
  coef_CI_par(fit,alpha = 0.05),
  coef_CI_C(fit, alpha = 0.05),
  check = FALSE)
)

ggplot2::autoplot(b1)
```

### The C++ version was only about 5 times faster than the R version. The C++ uses 1/7 as much memory as the R version. Also note that the C++ version calculates the quantiles differently from the R version. Therefore, the lower and upper bounds are slightly different in the C++ and R versions.

# 95% Prediction Interval (with n = 100 and p = 14 (original dataset has 1000 replications and 10 subsets))

```{r prediction interval, cache = TRUE}
plan(multiprocess, workers = 4)
PI(fit, dat2[1:3, 1:14], alpha = 0.05)
PI_par(fit, dat2[1:3, 1:14], alpha = 0.05)
PI_C(fit, dat2[1:3, 1:14], alpha = 0.05)

(b2 = bench::mark(
  PI(fit, dat2[1:3, 1:14], alpha = 0.05),
  PI_par(fit, dat2[1:3, 1:14], alpha = 0.05),
  PI_C(fit, dat2[1:3, 1:14], alpha = 0.05),
  check = FALSE)
)

ggplot2::autoplot(b2)
```

### The C++ version to calculate the 100 95% confidence intervals was more than 20 times faster than the R version. Again, the C++ and R confidence intervals are slightly difference due to calculating the quantiles differently.

# 95 % Confindence Interval for Variance (original dataset has 1000 replications and 10 subsets)

```{r variance interval, cache = TRUE}
s2_CI(fit, alpha = 0.05)
s2_CI_par(fit, alpha = 0.05)
s2_CI_C(fit, alpha = 0.05)

(b3 = bench::mark(
  s2_CI(fit, alpha = 0.05),
  s2_CI_par(fit, alpha = 0.05),
  s2_CI_C(fit, alpha = 0.05),
  check = FALSE)
)

ggplot2::autoplot(b3)
```



### The C++ version is about 19 times faster than the R version. The parallel version is not optimal for this case as it takes 100 times longer than the non-parallel R version. For some reason, the parallel version is not found to be faster than the non-parallel version for any of the 4 functions. But the C++ function is much faster anyways, so that is the one to use when trying to calculate these as fast as possible.



